### 2019-12-16 paper/introduction.tex
Intro startes

The \gls{GIF} \cite{doe2002technology} determined six innovative reactor systems: the Very High-Temperature Reactor (VHTR), the \gls{MSR}, the Supercritical Water-Cooled Reactor (SWCR), the Gas-cooled Fast Reactor (GFR), the Sodium-cooled Fast Reactor (SFR), and the Lead-cooled Fast Reactor (LFR). The MSR is the only liquid-fueled reactor among these reactors. Major nuclear centers pursue MSRs with renewed interest \cite{betzler_impacts_2019,ashraf2019whole_core,betzler2016modeling,mohsin2019safety,zhang2020radiotoxicity}. The MSR is a promising technology because of its dynamics, especially for thorium fuel utilization. However, this technology has challenges in safety, online reprocessing, and fuel handling. Safety is one of the technological goals of the MSR systems that require further research and investigation. The unique characteristics of the MSRs (liquid fuel, flux level, neutron economy, etc.) strongly affect its control system design. Graphite-moderated MSRs have a negative temperature coefficient of reactivity \cite{robertson_conceptual_1971,nuttin2005potential,rykhlevskii2019modeling,ashraf2019whole_core}. Doppler effect and thermal expansion of the fuel reduce core reactivity when the core heats up. However, graphite thermal expansion positively affect the core reactivity \cite{mathieu2006thorium}. The graphite expansion is not a dominating factor, thus core reactivity will decrease automatically when the core heats up \cite{li_optimization_2018}. MSR designs have a drain tank(s) to collect the liquid fuel in an emergency case. A freeze plug, which located under the core, melts when the temperature reaches a critical point. Then the fuel moves to the drain tank to shut down the reactor \cite{elsheikh2013safety}.

>>>>

The \gls{GIF} \cite{doe2002technology} determined six innovative reactor 
systems: the Very High-Temperature Reactor (VHTR), the \gls{MSR}, the 
Supercritical Water-Cooled Reactor (SWCR), the Gas-cooled Fast Reactor (GFR), 
the Sodium-cooled Fast Reactor (SFR), and the Lead-cooled Fast Reactor (LFR). 
The MSR is the only liquid-fueled reactor among these reactors. Major nuclear 
centers pursue MSRs with renewed interest \cite{betzler_impacts_2019, 
ashraf2019whole_core,betzler2016modeling,mohsin2019safety,zhang2020radiotoxicity}.
 The MSR is a promising technology because of its dynamics, especially for 
thorium fuel utilization. However, this technology has difficulties in safety, 
online reprocessing, and fuel handling. Safety is one of the primary goals of 
the MSR systems, which was understudied and require further investigation. The 
unique characteristics of the MSRs (liquid fuel, flux level, neutron economy, 
etc.) strongly affect its control system design. Graphite-moderated MSRs have a 
negative total temperature coefficient of reactivity 
\cite{robertson_conceptual_1971,nuttin2005potential,rykhlevskii2019modeling,ashraf2019whole_core}.
 Doppler effect and thermal expansion of the fuel reduce core reactivity when 
the core heats up. However, graphite thermal expansion positively affect the 
core reactivity \cite{mathieu2006thorium}. The graphite expansion is not a 
dominating factor, thus core reactivity will decrease automatically when the 
core heats up \cite{li_optimization_2018}. MSR designs have a drain tank(s) to 
collect the liquid fuel in an emergency case. A freeze plug, which located 
under the core, melts when the temperature reaches a critical point. Then the 
fuel moves to the drain tank to shut down the reactor \cite{elsheikh2013safety}.
